Ligeti, Stockhausen and Koenig:\\Aesthetics of Electronic Music

### 2015-09-23 manuscript.tex
Reindent 'itemize' to 2 spaces
Structural changes, Stockhausen & Koenig compositions + research targets section and more

\section{Introduction}
\label{sec:introduction}

@@

\section{Research Targets}  % Not sure that this is necessary
\label{sec:research_targets}

@@

Ligeti also refer to this ideas:

@@

\section{Compositions}
\label{sec:compositions}

\subsection{Ligeti: Remifications}
\label{sub:composition_ligeti}

@@

\subsubsection{Micropolyphony, flexible rhythm and misleading notation}

@@

\subsubsection{Machine like music / Meccanico-type}

@@

\subsubsection{Hectic quality / Gesticulation / Deep-frozen expressionism}

@@

\subsubsection{‘Mistiness’ to ‘clearing-up’ process}

@@

\subsection{Stockhausen: Gesang der J{\"u}nglinge}
\label{sub:composition_stockhausen}

\subsection{Koenig: TODO}
\label{sub:composition_koenig}

>>>>

\section{Introduction and targets}
\label{sec:introduction}

@@

@@

@@

TODO regarding the 2nd concept by stockhausen:
Ligeti also refer to this ideas:

\section{Ligeti's Remifications}
\label{sub:ramifications}

@@

\subsection*{Micropolyphony, flexible rhythm and misleading notation}

@@

\subsection*{Machine like music / Meccanico-type}

@@

\subsection*{Hectic quality / Gesticulation / Deep-frozen expressionism}

@@

\subsection*{‘Mistiness’ to ‘clearing-up’ process}

@@
